---
title: "Assignment3"
author: "RF"
date: "3/6/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(pacman)
p_load(rethinking, brms, tidyverse)

data <- read.csv('Assignment3Data.csv')

```

## Multivariate linear models

In this assignment you will investigate the relation between different aspects of IQ and symptom severity in ASD (as measured by ADOS). The assignment is meant to make you practice on linear models, multiple predictors and interactions.

The data you will use is the outcome of the psychological testing of the children you analyzed in methods 3.
Data: https://www.dropbox.com/s/hom2qnmp9hyfwmu/Assignment3Data.csv?dl=0

The data consists of ChildID, gender, age, diagnosis (ASD), symptom severity (ADOS), several aspects of IQ (NonVerbal/Perceptual,Verbal,Social) and the visit at which the tests were administered. 

The questions should be answered by focusing on visit 1.
```{r + Load data and prepare datasets}
#Data with only visit 1
visit1 <- data %>% filter(Visit == 1)

#Data only with vitist 1 and diagnosed with autism
V1_ASD <- visit1 %>% filter(ASD == 1)

```

The questions you will have to answer are:

1. Assess the relation between symptom severity and IQ (focus on visit 1 and children with ASD) and report the model, a plot of the model, a couple of lines describing the quality of the model and interpreting the results. 

P.S. Should you scale? 

P.P.S. Don't forget to motivate your priors. 

P.P.P.S. At least one plot for results and a plot for quality of each model (here and in the 
next questions) would be appreciated.

1.1. Verbal IQ and ADOS
```{r + VerbalIQ, Get prior}

#Raw Plot
V1_ASD %>% ggplot(aes(y = ADOS, x = VerbalIQ)) + 
  geom_smooth(method = 'lm', color = 'black') +
  geom_point(aes(color = ADOS))


plot(V1_ASD$ADOS ~ V1_ASD$VerbalIQ)

#Standardize predictors to a mean of 0 and sd of 1
V1_ASD$ADOS.s = (V1_ASD$ADOS - mean(V1_ASD$ADOS, na.rm = T))/ sd(V1_ASD$ADOS)
V1_ASD$VerbalIQ.s = (V1_ASD$VerbalIQ-mean(V1_ASD$VerbalIQ, na.rm = T))/sd(V1_ASD$VerbalIQ)

#Density
dens(V1_ASD$VerbalIQ.s)
dens(V1_ASD$ADOS.s)

#Model
m1_f <- bf(ADOS.s ~ 1 + VerbalIQ.s)

#Get prior
get_prior(m1_f, family = gaussian, V1_ASD)

mean(V1_ASD$ADOS.s)
mean(V1_ASD$VerbalIQ.s)

#Motivating priors
1/10^2
curve( dnorm( x , 0 , 0.5 ) , from=-3 , to=3 )


#Set prior (using normal not student_t)

prior = c(prior(normal(0, 0.5), class = 'Intercept'),  prior(normal(0, 0.5), class = 'b'), prior(normal(0,1), class = 'sigma'))

m1_prior <- brm(m1_f, family = gaussian, V1_ASD, prior = prior, sample_prior = 'only', chain =1 )

pp_check(m1_prior, nsamples = 100)

```


```{r + MAP, VerbalIQ, plots}

#MAP
flist <-  alist(
    ADOS.s ~ dnorm(mu , sigma),
    mu <- a + b*VerbalIQ.s ,
        a ~ dnorm(0 , 0.5 ),
        b ~ dnorm(0 , 0.5 ),
        sigma ~ dunif(0,0.8)
  )

m1.1 <- rethinking::map(flist, data = V1_ASD)

precis(m1.1)
precis_plot(precis(m1.1))


#Extract sample from the model
post.samples=extract.samples(m1.1)

#plotting with the uncertainty, does our model make sense?
plot(ADOS.s ~ VerbalIQ.s, V1_ASD)
abline(a=coef(m1.1)['a'], b=coef(m1.1)['b'])
for ( i in 1:150 )
abline( a=post.samples$a[i] , b=post.samples$b[i] , col=col.alpha(rangi2, 0.2) )

#Look at the distribution of mu
VerbalIQ.s.seq <- seq( from=-2 , to=2.5 , by=0.1 )

#Link-function to compute mu for each sample from posterior and for each value in the sequence
mu <- link(m1.1 , data=data.frame(VerbalIQ.s=VerbalIQ.s.seq) )

# use type="n" to hide raw data
plot( ADOS.s ~ VerbalIQ.s , V1_ASD , type="n" )
# loop over samples and plot each mu value
for ( i in 1:nrow(mu) )
points( VerbalIQ.s.seq , mu[i,] , pch=16 , col=col.alpha(rangi2,0.1) )


#summarize the distribution of mu
mu.mean <- apply( mu , 2 , mean )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )


#Plotting posterior prediction

# plot raw data
# fading out points to make line and interval more visible
plot( ADOS.s ~ VerbalIQ.s , data=V1_ASD , col=col.alpha(rangi2,0.5) )
# plot the MAP line, aka the mean mu for each weight
lines( VerbalIQ.s.seq , mu.mean )
# plot a shaded region for 89% HPDI
shade( mu.HPDI , VerbalIQ.s.seq )


#simulating ADOS values for the specific VerbalIQ values in the sequence
sim.ados <- sim( m1.1 , data=list(VerbalIQ.s=VerbalIQ.s.seq) )

#summarizing the distribution of the simulation
ados.HPDI <- apply( sim.ados , 2 , HPDI , prob=0.89 )

# plot raw data
plot( ADOS.s ~ VerbalIQ.s , V1_ASD , col=col.alpha(rangi2,0.5) )

#MAP line
lines( VerbalIQ.s.seq , mu.mean )
#HPDI region for line
shade( mu.HPDI , VerbalIQ.s.seq )
#PI region for simulated heights
shade( ados.HPDI , VerbalIQ.s.seq )


```

1.2. Non Verbal IQ and ADOS
```{r + MAP, Nonverbal, plots}

#Raw plot
plot(V1_ASD$ADOS ~ V1_ASD$NonVerbalIQ)

#Standardize
V1_ASD$NonVerbalIQ.s = (V1_ASD$NonVerbalIQ-mean(V1_ASD$NonVerbalIQ, na.rm = T))/sd(V1_ASD$NonVerbalIQ)

#Model
m2_f <- bf(ADOS.s ~ 1 + NonVerbalIQ.s)

#Get prior
get_prior(m2_f, family = gaussian, V1_ASD)

#Set prior (using normal not student_t)
#prior = c(prior(normal(0, 0.5), class = 'Intercept'),  prior(normal(0, 1), class = 'b'), prior(normal(0,3), class = 'sigma'))

#m2_prior <- brm(m1_f, family = gaussian, V1_ASD, prior = prior, sample_prior = 'only', chain =1 )

#pp_check(m2_prior, nsamples = 100)


#MAP

flist <-  alist(
    ADOS.s ~ dnorm(mu , sigma),
    mu <- a + b*NonVerbalIQ.s ,
        a ~ dnorm( 0 , 0.5 ) ,
        b ~ dnorm( 0 , 0.5 ) ,
        sigma ~ dunif( 0 , 1 )
  )

m1.2 <- rethinking::map(flist, data = V1_ASD)

precis(m1.2)
precis_plot(precis(m1.2))

pp_check(m1.2, nsample = 1000)

#Extract sample from the model
post.samples=extract.samples(m1.2)

#plotting with the uncertainty
#does our model if the model makes sense?
plot(ADOS.s ~ NonVerbalIQ.s, V1_ASD)
abline(a=coef(m1.2)['a'], b=coef(m1.2)['b'])
for ( i in 1:150 )
abline( a=post.samples$a[i] , b=post.samples$b[i] , col=col.alpha(rangi2, 0.2) )

#Look at the distribution of mu
NonVerbalIQ.s.seq <- seq( from=-3 , to=3 , by=0.1 )

#Link-function to compute mu for each sample from posterior and for each value in the sequence
mu <- link(m1.2 , data=data.frame(NonVerbalIQ.s=NonVerbalIQ.s.seq) )


# use type="n" to hide raw data
plot( ADOS.s ~ NonVerbalIQ.s , V1_ASD , type="n" )
# loop over samples and plot each mu value
for ( i in 1:nrow(mu) )
points( NonVerbalIQ.s.seq , mu[i,] , pch=16 , col=col.alpha(rangi2,0.1) )


#summarize the distribution of mu
mu.mean <- apply( mu , 2 , mean )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )


#Plotting posterior prediction


# plot raw data
# fading out points to make line and interval more visible
plot( ADOS.s ~ NonVerbalIQ.s , data=V1_ASD , col=col.alpha(rangi2,0.5) )
# plot the MAP line, aka the mean mu for each weight
lines( NonVerbalIQ.s.seq , mu.mean )
# plot a shaded region for 89% HPDI
shade( mu.HPDI , NonVerbalIQ.s.seq )


```

1.3. Social IQ and ADOS
```{r + MAP, social, plots}
#Raw plot
plot(V1_ASD$ADOS ~ V1_ASD$SocialIQ)

#Standardize
V1_ASD$SocialIQ.s = (V1_ASD$SocialIQ-mean(V1_ASD$SocialIQ, na.rm = T))/sd(V1_ASD$SocialIQ)


#MAP
flist <-  alist(
    ADOS.s ~ dnorm(mu , sigma),
    mu <- a + b*SocialIQ.s ,
        a ~ dnorm( 0 , 0.5 ) ,
        b ~ dnorm( 0 , 0.5 ) ,
        sigma ~ dunif( 0 , 1 )
  )

m1.3 <- rethinking::map(flist, data = V1_ASD)

precis(m1.3)
precis_plot(precis(m1.3))


#Extract sample from the model
post.samples=extract.samples(m1.3)

#plotting with the uncertainty, does our model make sense?
plot(ADOS.s ~ SocialIQ.s, V1_ASD)
abline(a=coef(m1.3)['a'], b=coef(m1.3)['b'])
for ( i in 1:150 )
abline( a=post.samples$a[i] , b=post.samples$b[i] , col=col.alpha(rangi2, 0.2) )

#Look at the distribution of mu
SocialIQ.s.seq <- seq( from=-2 , to=3 , by=0.1 )

#Link-function to compute mu for each sample from posterior and for each value in the sequence
mu <- link(m1.3 , data=data.frame(SocialIQ.s=SocialIQ.s.seq) )

#Plot
plot( ADOS.s ~ SocialIQ.s , V1_ASD , type="n" )
for ( i in 1:nrow(mu) )
points( SocialIQ.s.seq , mu[i,] , pch=16 , col=col.alpha(rangi2,0.1) )

#summarize the distribution of mu
mu.mean <- apply( mu , 2 , mean )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )


#Plotting posterior prediction
plot( ADOS.s ~ SocialIQ.s , data=V1_ASD , col=col.alpha(rangi2,0.5) )
lines( SocialIQ.s.seq , mu.mean )
shade( mu.HPDI , SocialIQ.s.seq )

```

###2. Do the different aspects of IQ account for different portions of the variance in ADOS? 

##2.1. Does it make sense to have all IQ measures in the same model? First write a few lines answering the question and motivating your answer, including a discussion as to what happens when you put all of them in the same model. Then build a model following your answer. If your answer is "no", you are not free, you still have to answer: are there alternative ways of answering the question?

##2.2. Build the model, assess its quality, write a few lines interpreting the results.
```{r + Ados ~ All IQ meassures}
#MAP
flist <-  alist(
    ADOS.s ~ dnorm(mu , sigma),
    mu <- a + bs*SocialIQ.s + bv*VerbalIQ.s + bn*NonVerbalIQ.s,
        a ~ dnorm( 0 , 0.5 ) ,
        bs ~ dnorm( 0 , 0.5 ) ,
        bv ~ dnorm( 0 , 0.5 ), 
        bn ~ dnorm(0, 0.5 ),
        sigma ~ dunif( 0 , 0.8 )
  )

m2.1 <- rethinking::map(flist, data = V1_ASD)

precis(m2.1)
precis_plot(precis(m2.1))

#Extract sample from the model
post.samples=extract.samples(m2.1)

plot(bs ~ bn, post.samples, col = col.alpha(rangi2,0.1), pch = 16)
plot(bs ~ bv, post.samples, col = col.alpha(rangi2,0.1), pch = 16)
plot(bn ~ bv, post.samples, col = col.alpha(rangi2,0.1), pch = 16)


#plotting with the uncertainty
#does our model if the model makes sense?
plot(ADOS.s ~ SocialIQ.s + NonVerbalIQ.s + VerbalIQ.s, V1_ASD)
abline(a=coef(m2.1)['a'], b=coef(m2.1)['bs']+coef(m2.1)['bn']+coef(m2.1)['bv'])
for ( i in 1:150 )
abline( a=post.samples$a[i] , b=post.samples$bs[i]+post.samples$bn[i]+post.samples$bv[i] , col=col.alpha(rangi2, 0.2) )


####5.11 i Rethinking

#Link-function to compute mu for each sample from posterior and for each value in the sequence
mu <- link(m2.1)

#summarize the across cases
mu.mean <- apply( mu , 2 , mean )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )

#Plotting (5.12)
plot( mu.mean ~ V1_ASD$ADOS.s , col=rangi2 , ylim=range(mu.HPDI) ,
xlab="Observed ADOS" , ylab="Predicted ADOS" )
abline( a=0 , b=1 , lty=2 )
for ( i in 1:nrow(V1_ASD) )
lines( rep(V1_ASD$ADOS.s[i],2) , c(mu.HPDI[1,i],mu.HPDI[2,i]) ,
col=rangi2 )

#5.13
#identify( x=V1_ASD$ADOS.s , y=mu.mean , labels=V1_ASD$ChildID , cex=0.8 )


```

###3. Let's now include also the TD children. 

Does it make sense to ask whether IQ and ADOS are related? Motivate your answer. 

In any case, if you wanted to build a model to answer that question, which model would you build? Run the model, assess its quality, write a few lines interpreting the results.
```{r + Model with both TD and ASD}
#Standardize predictors to a mean of 0 and sd of 1

visit1 <- na.omit(visit1)

visit1$ADOS.s = (visit1$ADOS - mean(visit1$ADOS))/ sd(visit1$ADOS)

visit1$VerbalIQ.s = (visit1$VerbalIQ - mean(visit1$VerbalIQ, na.rm = T))/sd(visit1$VerbalIQ)

visit1$NonVerbalIQ.s = (visit1$NonVerbalIQ - mean(visit1$NonVerbalIQ, na.rm = T))/sd(visit1$NonVerbalIQ)

visit1$SocialIQ.s = (visit1$SocialIQ-mean(visit1$SocialIQ, na.rm = T))/sd(visit1$SocialIQ)


#Model
flist <-  alist(
    ADOS.s ~ dnorm(mu , sigma),
    mu <- a + bV*VerbalIQ.s + bN*NonVerbalIQ.s + bS*SocialIQ.s ,
        a ~ dnorm( 0 , 0.5 ) ,
        bV ~ dnorm( 0 , 0.5 ) ,
        bN ~ dnorm( 0 , 0.5 ) ,
        bS ~ dnorm( 0 , 0.5 ) ,
        sigma ~ dunif( 0 , 0.8 )
  )

m3.1 <- rethinking::map(flist, data = visit1)

precis(m3.1)
precis_plot( precis(m3.1))



####5.11 i Rethinking

#Link-function to compute mu for each sample from posterior and for each value in the sequence
mu <- link(m3.1)

#summarize the across cases
mu.mean <- apply( mu , 2 , mean )
mu.HPDI <- apply( mu , 2 , HPDI , prob=0.89 )


#Plotting (5.12)
plot( mu.mean ~ visit1$ADOS.s , col= ('black') , ylim=range(mu.HPDI) ,
xlab="Observed ADOS" , ylab="Predicted ADOS" )
abline( a=0 , b=1 , lty=2 )
for ( i in 1:nrow(visit1) )
lines( rep(visit1$ADOS.s[i],2) , c(mu.HPDI[1,i],mu.HPDI[2,i]) ,
col=rangi2 )

#5.13
#identify( x=visit1$ADOS.s , y=mu.mean , labels=visit1$ChildID , cex=0.8 )


```


```{r + Interaction?}

#Is there an interaction 

#checking with plots 
ggplot(visit1, aes(NonVerbalIQ, ADOS, color = ASD)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "ADOS score by non-verbal IQ for ASD and TD") 


ggplot(visit1, aes(VerbalIQ, ADOS, color = ASD)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "ADOS score by verbal IQ for ASD and TD") 

ggplot(visit1, aes(SocialIQ, ADOS, color = ASD)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(title = "ADOS score by social IQ for ASD and TD")

```

###4. Let's discuss contents:
##4.1. You have three scores for IQ, do they show shared variance? Is that the same in TD and ASD? What does that tell us about IQ?


```{r + Correlation + ASD only, TD only}

V1_TD <- visit1 %>% filter(ASD == 0)
V1_TD <- (na.omit(V1_TD))

V1_TD$ADOS.s = (V1_TD$ADOS - mean(V1_TD$ADOS))/ sd(V1_TD$ADOS)

V1_TD$VerbalIQ.s = (V1_TD$VerbalIQ - mean(V1_TD$VerbalIQ, na.rm = T))/sd(V1_TD$VerbalIQ)

V1_TD$NonVerbalIQ.s = (V1_TD$NonVerbalIQ - mean(V1_TD$NonVerbalIQ, na.rm = T))/sd(V1_TD$NonVerbalIQ)

V1_TD$SocialIQ.s = (V1_TD$SocialIQ-mean(V1_TD$SocialIQ, na.rm = T))/sd(V1_TD$SocialIQ)


cor(select(V1_ASD, VerbalIQ.s, NonVerbalIQ.s, SocialIQ.s, ADOS.s))
cor(select(V1_TD, VerbalIQ, NonVerbalIQ, SocialIQ))

```

```{r + Residual ASD plots}
#Map
flist <-  alist(
    ADOS.s ~ dnorm(mu , sigma),
    mu <- a + bV*VerbalIQ.s + bN*NonVerbalIQ.s + bS*SocialIQ.s ,
        a ~ dnorm( 0 , 0.5 ) ,
        bV ~ dnorm( 0 , 0.5 ) ,
        bN ~ dnorm( 0 , 0.5 ) ,
        bS ~ dnorm( 0 , 0.5 ) ,
        sigma ~ dunif( 0 , 0.8 )
  )

m1.4 <- rethinking::map(flist, data = V1_ASD)
precis(m1.4)
precis_plot( precis(m1.4))



#Model for residuals of verbalIQ 'controlling' for NonVerbalIQ and SocialIQ
modelVIQ <- rethinking::map(
  alist(
    VerbalIQ.s ~ dnorm(mu, sigma),
    mu <- a + b1*NonVerbalIQ.s + b2*SocialIQ.s,
    a ~ dnorm(0,0.5),
    b1 ~ dnorm(0, 0.5),
    b2 ~ dnorm(0, 0.5),
    sigma ~ dunif(0, 0.8)
  ),
  data = V1_ASD)


#creating model for residuals of non-verbalIQ 'controlling' for VIQ and SIQ
modelNonVIQ <- rethinking::map(
  alist(
    NonVerbalIQ.s ~ dnorm(mu, sigma),
    mu <- a + b1*VerbalIQ.s + b2*SocialIQ.s,
    a ~ dnorm(0,0.5),
    b1 ~ dnorm(0, 0.5),
    b2 ~ dnorm(0, 0.5),
    sigma ~ dunif(0, 0.8)
  ),
  data = V1_ASD)

#creating model for residuals of social IQ 'controlling' for NVIQ and VIQ
modelSocIQ <- rethinking::map(
  alist(
    SocialIQ.s ~ dnorm(mu, sigma),
    mu <- a + b1*NonVerbalIQ.s + b2*VerbalIQ.s,
    a ~ dnorm(0, 0.5),
    b1 ~ dnorm(0, 0.5),
    b2 ~ dnorm(0, 0.5),
    sigma ~ dunif(0, 0.8)
  ),
  data = V1_ASD)



#Residuals

#VERBAL
mu.v <- coef(modelVIQ)['a'] + coef(modelVIQ)['b1']*V1_ASD$NonVerbalIQ.s + coef(modelVIQ)['b2']*V1_ASD$SocialIQ.s
#compute residual for each value
resid_verbal <- V1_ASD$VerbalIQ.s - mu.v
  

#SOCIAL
mu.s <- coef(modelSocIQ)['a'] + coef(modelSocIQ)['b1']*V1_ASD$NonVerbalIQ.s + coef(modelSocIQ)['b2']*V1_ASD$VerbalIQ.s
#compute residual for each value
resid_social <- V1_ASD$SocialIQ.s - mu.s
  

#NONVERBAL
mu.n <- coef(modelNonVIQ)['a'] + coef(modelNonVIQ)['b1']*V1_ASD$VerbalIQ.s + coef(modelNonVIQ)['b2']*V1_ASD$SocialIQ.s
#compute residual for each value
resid_nonverbal <- V1_ASD$NonVerbalIQ.s - mu.n
  
  
  
#Dataframes
VerbalIQ_df = data.frame(resid_verbal, V1_ASD$ADOS.s)
NonVerbalIQ_df = data.frame(resid_nonverbal, V1_ASD$ADOS.s)
SocialIQ_df = data.frame(resid_social, V1_ASD$ADOS.s)

resplot_verbal = ggplot(VerbalIQ_df, aes(resid_verbal, V1_ASD.ADOS.s)) +
  geom_point(aes(colour = palette(rainbow(34)))) +
  geom_smooth(method='lm', col = 'black') +
  geom_vline(xintercept=0, linetype = 'dotted') + theme_grey() + theme(legend.position = 'none')+
  xlab('Residuals for Verbal "controlling" for social and nonverbal')+
  ylab('Ados (Standardized)')

resplot_verbal

resplot_Nonverbal = ggplot(NonVerbalIQ_df, aes(resid_nonverbal, V1_ASD.ADOS.s)) +
  geom_point(aes(colour = palette(rainbow(34)))) +
  geom_smooth(method='lm', col = 'black') +
  geom_vline(xintercept=0, linetype = 'dotted') + theme_grey() + theme(legend.position = 'none') + 
  xlab('Residuals for Nonverbal IQ "controlling" for social and verbal')+
  ylab('Ados (Standardized)')

resplot_social = ggplot(SocialIQ_df, aes(resid_social, V1_ASD.ADOS.s)) +
  geom_point(aes(colour = palette(rainbow(34)))) +
  geom_smooth(method='lm', col = 'black') +
  geom_vline(xintercept=0, linetype = 'dotted') + theme_grey() + theme(legend.position = 'none') + 
  xlab('Residuals for Social IQ "controlling" for verbal and nonverbal')+
  ylab('Ados (Standardized)')


resplot_verbal
resplot_Nonverbal
resplot_social
  
  

```

```{r + Residual plots only TD}

#Model for residuals of verbalIQ 'controlling' for NonVerbalIQ and SocialIQ
modelVIQ <- rethinking::map(
  alist(
    VerbalIQ.s ~ dnorm(mu, sigma),
    mu <- a + b1*NonVerbalIQ.s + b2*SocialIQ.s,
    a ~ dnorm(0,0.5),
    b1 ~ dnorm(0, 0.5),
    b2 ~ dnorm(0, 0.5),
    sigma ~ dunif(0, 0.8)
  ),
  data = V1_TD)


#creating model for residuals of non-verbalIQ 'controlling' for VIQ and SIQ
modelNonVIQ <- rethinking::map(
  alist(
    NonVerbalIQ.s ~ dnorm(mu, sigma),
    mu <- a + b1*VerbalIQ.s + b2*SocialIQ.s,
    a ~ dnorm(0,0.5),
    b1 ~ dnorm(0, 0.5),
    b2 ~ dnorm(0, 0.5),
    sigma ~ dunif(0, 0.8)
  ),
  data = V1_TD)

#creating model for residuals of social IQ 'controlling' for NVIQ and VIQ
modelSocIQ <- rethinking::map(
  alist(
    SocialIQ.s ~ dnorm(mu, sigma),
    mu <- a + b1*NonVerbalIQ.s + b2*VerbalIQ.s,
    a ~ dnorm(0,0.5),
    b1 ~ dnorm(0, 0.5),
    b2 ~ dnorm(0, 0.5),
    sigma ~ dunif(0, 0.8)
  ),
  data = V1_TD)


#Residuals

#VERBAL
mu.v <- coef(modelVIQ)['a'] + coef(modelVIQ)['b1']*V1_TD$NonVerbalIQ.s + coef(modelVIQ)['b2']*V1_TD$SocialIQ.s
#compute residual for each value
resid_verbal <- V1_TD$VerbalIQ.s - mu.v
  

#SOCIAL
mu.s <- coef(modelSocIQ)['a'] + coef(modelSocIQ)['b1']*V1_TD$NonVerbalIQ.s + coef(modelSocIQ)['b2']*V1_TD$VerbalIQ.s
#compute residual for each value
resid_social <- V1_TD$SocialIQ.s - mu.s
  

#NONVERBAL
mu.n <- coef(modelNonVIQ)['a'] + coef(modelNonVIQ)['b1']*V1_TSD$VerbalIQ.s + coef(modelNonVIQ)['b2']*V1_TD$SocialIQ.s
#compute residual for each value
resid_nonverbal <- V1_TD$NonVerbalIQ.s - mu.n
  
  
  
#Dataframes
VerbalIQ_df = data.frame(resid_verbal, V1_TD$ADOS.s)
NonVerbalIQ_df = data.frame(resid_nonverbal, V1_TD$ADOS.s)
SocialIQ_df = data.frame(resid_social, V1_TD$ADOS.s)

resplot_verbal = ggplot(VerbalIQ_df, aes(resid_verbal, V1_TD.ADOS.s)) +
  geom_point(aes(colour = palette(rainbow(36)))) +
  geom_smooth(method='lm', col = 'black') +
  geom_vline(xintercept=0, linetype = 'dotted') + theme_grey() + theme(legend.position = 'none') + 
  xlab('Residuals for Verbal "controlling" for social and nonverbal')+
  ylab('Ados (Standardized)')
  

resplot_Nonverbal = ggplot(NonVerbalIQ_df, aes(resid_nonverbal, V1_TD.ADOS.s)) +
  geom_point(aes(colour = palette(rainbow(36)))) +
  geom_smooth(method='lm', col = 'black') +
  geom_vline(xintercept=0, linetype = 'dotted', col = 'black')+ theme_grey() + theme(legend.position = 'none') + 
xlab('Residuals for Nonverbal IQ "controlling" for social and verbal')+
  ylab('Ados (Standardized)')

resplot_social = ggplot(SocialIQ_df, aes(resid_social, V1_TD.ADOS.s)) +
  geom_point(aes(colour = palette(rainbow(36)))) +
  geom_smooth(method='lm', col = 'black') +
  geom_vline(xintercept=0, linetype = 'dotted')+ theme_grey() + theme(legend.position = 'none') + 
  xlab('Residuals for Social IQ "controlling" for verbal and nonverbal')+
  ylab('Ados (Standardized)')


resplot_verbal
resplot_Nonverbal
resplot_social

```

ASD children: 
Social IQ & Verbal IQ are the strongest predictors of ADOS scores
(redsidual plot)

Verbal IQ correlated with both Non-Verbal & Social IQ (more than 0.6)
Social & Non-Verbal IQ are not very correlated. 

TD children: 
Non-Verbal and Verbal IQ are highly correlated (0.55)
Social IQ is not really corrleated with any of them. 
Opposite effect on between social and nonverbal


##4.2. You have explored the relation between IQ and ADOS. How do you explain that relation from a cognitive perspective? N.B. You can present alternative hypotheses.

5. Bonus questions: Including measurement errors. 
5.1. Let's assume that ADOS has a measurement error of 1. How would you model that in any of the previous models? 
5.2. We know that IQ has an estimated measurement error of 2.12. How would you include that? 


